%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Keenan Wulff}
\href{mailto:keenan.wulff@colorado.edu}{keenan.wulff@colorado.edu} | 303-709-4611 \\
\hrulefill \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.4\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Colorado Boulder}
\descript{Electrical and Computer Engineering}
\descript{Physics Minor}
\location{Expected May 2019}
College of Engineering \\
\location{ Cum. GPA: 3.42 / 4.0 }
\sectionsep

\subsection{Evergreen High School}
\location{Grad. May 2015}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% * <kewu4568@colorado.edu> 2017-10-08T05:59:56.340Z:
% 
% Should  Coursework be on main column?
% 
% ^.
\section{Coursework and Skills}
\subsection{Programming}
\begin{minipage}[t]{.35\textwidth}
\location{Proficient}
\begin{tightemize}
\item C
\item C++
\item Matlab 
\item Python 
\end{tightemize}
\end{minipage}
\begin{minipage}[t]{.44\textwidth}
\location{Familiar}
\begin{tightemize}
\item RISC Assembly 
\item Latex
\item Verilog 
\item Mathematica
\end{tightemize}
\end{minipage}
\sectionsep

\subsection{Analog Design}
\vspace*{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Linear circuits, plus MOSFET, BJT, diode, and Op-Amp operation.
\item Laplace and Fourier analysis, with study of active and passive filters.
\item Familiarity with LTSpice.
\end{tightemize}
\sectionsep

\subsection{Digital Design}

\vspace*{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Boolean algebra, logic gates, and optimization.
\item Work with state machines and Verilog.
\item Computer Architecture

\end{tightemize}
\sectionsep

\subsection{Embedded Design}
\vspace*{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Knowledge of CPU structure and program flow.
\item Use of ARM Cortex processors with appropriate debugging tools.
\item Work with UART, matrix scanning, interrupt subroutines, BLE, timers, and buffers
\item Knowledge of operating system concepts like scheduling, thread and process management, and safe memory management.
\end{tightemize}
\sectionsep

\subsection{Physics}
\vspace*{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Classical mechanics.
\item Electromagnetic fields and waves.
\item Special relativity.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.59\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\summary{
Combines electrical engineering, computer engineering, and physics knowledge to understand and dissect large problems. Able to positively contribute in fast-paced team environments
}
\section{Experience}

\runsubsection{University of Colorado Boulder}
\descript{| Research Assistant}
\location{August 2017 - July 2018 | Boulder, CO}
\begin{tightemize}
\vspace*{1.2\topsep}
\item Working with Information Sciences Department to investigate online social media trends.
\item Using Python to interact with online APIs and utilizing
database querying.
\end{tightemize}
\sectionsep

\runsubsection{Toys2Life}
\descript{| Firmware Engineering Intern}
\location{June 2017 - August 2017 | Boulder, CO}
\begin{tightemize}
\item Worked to port firmware onto ARM Cortex based microcontroller.
\item Utilized BLE advertising to assemble a proximity matrix between several microcontrollers.
\end{tightemize}
\sectionsep

\runsubsection{University of Colorado Boulder}
\descript{| Learning Assistant }
\location{August 2016 - May 2017 | Boulder, CO}
\begin{tightemize}
\item Worked in Physics Department to help students understand the conceptual base of classical mechanics and electromagnetism.
\item Learned pedagogical methods and communication skills.
\end{tightemize}
\sectionsep

\runsubsection{Bentley Systems}
\descript{| Software Engineering Intern}
\location{June 2016 - August 2016 | Greenwood Village, CO}
\begin{tightemize}
\item Worked in a team to improve truck routing software used by a state government.
\end{tightemize}
\sectionsep

\runsubsection{Walgreens}
\descript{| Customer Service Associate}
\location{June 2014 - August 2015 | Evergreen, CO}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurriculars}
\runsubsection{Engineers Without Borders -- CU Nepal}
\descript{| Participant and Design Team Member}
\location{Aug 2015 - Present | Boulder, CO}
\begin{tightemize}
\item Worked to design roughing filter and spring source protection for Nepali community.  Helped ensure sustainability.
\end{tightemize}
\sectionsep

\runsubsection{Rise Percussion}
\descript{| Mallet Percussion}
\location{October 2014 - Present | Denver CO}
\begin{tightemize}
\item Several awards, including second place in WGI Open class, and Semi-finalist in WGI World Class
\end{tightemize}
\sectionsep



\end{minipage} 
\end{document}  \documentclass[]{article}